### 2025-04-23 evaluating-prediction-accuracy.qmd
20250421 - update figure caption for calibration plots
20250423 - reorganize
20250423 - prediction of touchdowns vs yards

@@

[EVALUATE EMPIRICALLY]

@@

To evaluate the accuracy of projections, we must first merge projections with actual performance.

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyOverall
#| fig-cap: "Calibration Plot for Weekly Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyQBs
#| fig-cap: "Calibration Plot for Weekly Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyRBs
#| fig-cap: "Calibration Plot for Weekly Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyWRs
#| fig-cap: "Calibration Plot for Weekly Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyTEs
#| fig-cap: "Calibration Plot for Weekly Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyKs
#| fig-cap: "Calibration Plot for Weekly Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDLs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyLBs
#| fig-cap: "Calibration Plot for Weekly Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDBs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

>>>>

### Prepare Data {#sec-predictionAccuracyPrepareData}

#### Seasonal Projections {#sec-predictionAccuracyPrepareDataSeasonal}

To evaluate the accuracy of projections, we must first merge projections with actual performance.
Below, we merge seasonal projections with actual performance.

### Weekly Projections {#sec-predictionAccuracyPrepareDataWeekly}

Below, we merge weekly projections with actual performance.

@@

Here is the accuracy of the prediction of passing touchdowns versus passing yards among Quarterbacks:

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$pass_tds,
  actual = projectionsWithActuals_weekly_qb$passing_tds,
  dropUndefined = TRUE
)

petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$pass_yds,
  actual = projectionsWithActuals_weekly_qb$passing_yards,
  dropUndefined = TRUE
)
```

```{r}
#| include: false

rSquared_passTds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$pass_tds,
  actual = projectionsWithActuals_weekly_qb$passing_tds,
  dropUndefined = TRUE
)$rsquared

rSquared_passYds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_qb$pass_yds,
  actual = projectionsWithActuals_weekly_qb$passing_yards,
  dropUndefined = TRUE
)$rsquared
```

The accuracy for predicting passing yards ($R^2 = `r petersenlab::apa(rSquared_passYds, decimals = 2, leading = FALSE)`$) is higher than the accuracy for predicting passing touchdowns ($R^2 = `r petersenlab::apa(rSquared_passTds, decimals = 2, leading = FALSE)`$).

Here is the accuracy of the prediction of rushing touchdowns versus rushing yards among Running Backs:

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$rush_tds,
  actual = projectionsWithActuals_weekly_rb$rushing_tds,
  dropUndefined = TRUE
)

petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$rush_yds,
  actual = projectionsWithActuals_weekly_rb$rushing_yards,
  dropUndefined = TRUE
)
```

```{r}
#| include: false

rSquared_rushTds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$rush_tds,
  actual = projectionsWithActuals_weekly_rb$rushing_tds,
  dropUndefined = TRUE
)$rsquared

rSquared_rushYds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_rb$rush_yds,
  actual = projectionsWithActuals_weekly_rb$rushing_yards,
  dropUndefined = TRUE
)$rsquared
```

The accuracy for predicting rushing yards ($R^2 = `r petersenlab::apa(rSquared_rushYds, decimals = 2, leading = FALSE)`$) is higher than the accuracy for predicting rushing touchdowns ($R^2 = `r petersenlab::apa(rSquared_rushTds, decimals = 2, leading = FALSE)`$).

Here is the accuracy of the prediction of receiving touchdowns versus receiving yards among Wide Receivers:

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$rec_tds,
  actual = projectionsWithActuals_weekly_wr$receiving_tds,
  dropUndefined = TRUE
)

petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$rec_yds,
  actual = projectionsWithActuals_weekly_wr$receiving_yards,
  dropUndefined = TRUE
)
```

```{r}
#| include: false

rSquared_recTds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$rec_tds,
  actual = projectionsWithActuals_weekly_wr$receiving_tds,
  dropUndefined = TRUE
)$rsquared

rSquared_recYds <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_wr$rec_yds,
  actual = projectionsWithActuals_weekly_wr$receiving_yards,
  dropUndefined = TRUE
)$rsquared
```

The accuracy for predicting receiving yards ($R^2 = `r petersenlab::apa(rSquared_recYds, decimals = 2, leading = FALSE)`$) is higher than the accuracy for predicting rushing touchdowns ($R^2 = `r petersenlab::apa(rSquared_recTds, decimals = 2, leading = FALSE)`$) among Wide Receivers.

Here is the accuracy of the prediction of receiving touchdowns versus receiving yards among Tight Ends:

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$rec_tds,
  actual = projectionsWithActuals_weekly_te$receiving_tds,
  dropUndefined = TRUE
)

petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$rec_yds,
  actual = projectionsWithActuals_weekly_te$receiving_yards,
  dropUndefined = TRUE
)
```

```{r}
#| include: false

rSquared_recTds_te <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$rec_tds,
  actual = projectionsWithActuals_weekly_te$receiving_tds,
  dropUndefined = TRUE
)$rsquared

rSquared_recYds_te <- petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_weekly_te$rec_yds,
  actual = projectionsWithActuals_weekly_te$receiving_yards,
  dropUndefined = TRUE
)$rsquared
```

The accuracy for predicting receiving yards ($R^2 = `r petersenlab::apa(rSquared_recYds_te, decimals = 2, leading = FALSE)`$) is higher than the accuracy for predicting rushing touchdowns ($R^2 = `r petersenlab::apa(rSquared_recTds_te, decimals = 2, leading = FALSE)`$) among Tight Ends.

In sum, the proportion of variance explained by the prediction (i.e., $R^2$) is much higher for passing/rushing/receiving yards than it is for touchdowns.
This is consistent with the notion that prediction accuracy tends to be lower for lower [base rate](#sec-baseRate) events (like touchdowns) compared to higher [base rate](#sec-baseRate) events.

@@

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyOverall
#| fig-cap: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyQBs
#| fig-cap: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Quarterbacks. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyRBs
#| fig-cap: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Running Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyWRs
#| fig-cap: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Wide Receivers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyTEs
#| fig-cap: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Tight Ends. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyKs
#| fig-cap: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Kickers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDLs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Linemen. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyLBs
#| fig-cap: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Linebackers. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotWeeklyDBs
#| fig-cap: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Weekly Projections of Defensive Backs. The diagonal black line is the reference line representing perfect calibration. The yellow line is the best-fit line based on a generalized additive model. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 6
